\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amssymb}
\title{Math 208\\Test 1 - Problems}
\date{September 20, 2013}
\author{Jesus who creams your bagel}
\begin{document}
\maketitle
\begin{enumerate}
% Problem 1
	\item (15 Points) Find the general solution of the system \\
		$\left\{\begin{array}{rrrrrrrrrrr}
	   	 	x_1 & - & 2x_2 & + & x_3 & + & x_4 & + & x_5 & = & 2\\
	   	 	x_1 & - & 2x_2 & + & 2x_3 & - & x_4 & - & 2x_5 & = & 5\\
	   		 x_1 & - & 2x_2 & - & x_3 & + & 5x_4 & + & 7x_5 & = & 4\\
		\end{array}\right.$ \\
% Problem 2
	\item Let $\vec{a} =
	 	\left[ \begin{array}{r}
			3\\
			-1\\
			4\\
		\end{array}\right]$
		and $\vec{b} = 
		\left[\begin{array}{r}
			5\\
			-2\\
			1\\
		\end{array}\right]$. Find a parametric equation for the line\\
	\begin{enumerate}
	% Part (a)
		\item (5 Points) passing through (end-point of) $\vec{a}$ and parallel to $\vec{b}$;\\
	% Part (b)
		\item (5 Points) passing through the (end-points of) vectors $\vec{a}$ and $\vec{b}$\\
	\end{enumerate}
%  Problem 3
	\item Let $\left\{\begin{array}{rrrrrrrrr}
			7x_1&+&2x_2&+&3x_3&+&5x_4&=&4\\
			x_1&-&x_2&-&2x_3&+&x_4&=&7\\
			3x_1&+&x_2&&  &-&x_4&=&-3\\
		\end{array}\right.$
	\textbf{}{Do not solve the system!}\\
	\begin{enumerate}
	% Part (a)
		\item (5 Points) Vector form
	% Part (b)
		\item (5 Points) Matrix form 
	% Part (c)
		\item (5 Points) Augmented matrix form
	\end{enumerate}
% Problem 4 
	\item (15 Points) Consider the following linear system: 
		$\left\{\begin{array}{rrrrr}
			x_1&-&hx_2&=&3\\
			2x_1&+&4x_2&=&k\\
		\end{array}\right.$
	\begin{enumerate}
	% Part (a)
		\item (5 Points) Describe \textbf{all values} of $h$ and $k$ for which this system has exactly one solution.	
	% Part (b)
		\item (5 Points) Describe \textbf{all values} of $h$ and $k$ for which this system has infinitely many solutions.
	% Part (c)
		\item (5 Points) Describe \textbf{all values} of $h$ and $k$ for which this system is inconsistent.
	\end{enumerate}
% Problem 5
	\item (15 Points) Find the standard matrix of the transformation $T$, where $T : \mathbb{R}^2 \longrightarrow
	\mathbb{R}^2$ first rotates by the angle $\frac{\pi}{4}$ radians (counterclockwise) 
	and then reflects with respect to the line $x_1 + x_2 = 0$.
% Problem 6
	\item (15 Points) Find \textbf{all} values $\vec{a}$ and $\vec{b}$ for which the vectors 
		$\left[ \begin{array}{r}
			1\\
			0\\
			1\\
		\end{array}\right],
		\left[ \begin{array}{r}
			0\\
			1\\
			a\\
		\end{array}\right],
		\left[ \begin{array}{r}
			b\\
			1\\
			1\\
		\end{array}\right]$ are linearly dependent
% Problem 7
	\item (15 Points)
	 Let $T : \mathbb{R}^2 \longrightarrow \mathbb{R}^3$ be a linear transformation that maps  
		$\vec{u_1} = \left[\begin{array}{r}
		1\\
		-1\\
		\end{array}\right]$
	is
		$\vec{v_1} = \left[\begin{array}{r}
		1\\
		-2\\
		1\\
		\end{array}\right]$
	and maps
		$\vec{u_2} = \left[\begin{array}{r}
		2\\
		3\\
		\end{array}\right]$
	is
		$\vec{v_2} = \left[\begin{array}{r}
		-1\\
		1\\
		2\\
		\end{array}\right]$
	.Find the image of 
		$\vec{w} = \left[\begin{array}{r}
		1\\
		4\\
		\end{array}\right]$
	.
%Problem 8
	\item Let $T : \mathbb{R}^2 \longrightarrow \mathbb{R}^3$. Check which of the following transformations are linear and 			which are not. \textbf{The answer should be precisely justified!}
	\begin{enumerate}
	% Part (a)
		\item (5 Points)
			$T\left(\left[\begin{array}{r}
				x_1\\
				x_2\\
			\end{array}\right]\right) =
			\left[\begin{array}{rrc}
				x_1&+&3x_2\\
				x_2&+&1\\
				x_1\\
			\end{array}\right]$
	% Part (b)
		\item (5 Points)
			$T\left(\left[\begin{array}{r}
				x_1\\
				x_2\\
			\end{array}\right]\right) =
			\left[\begin{array}{rrr}
				x_1&+&x_2\\
				x_2&-&x_1\\
				x_1^2 &-&x_2\\
			\end{array}\right]$
	% Part (c)
		\item (5 Points)
			$T\left(\left[\begin{array}{r}
				x_1\\
				x_2\\
			\end{array}\right]\right) =
			\left[\begin{array}{rrc}
				x_1&+&2x_2\\
				x_2&-&x_1\\
				|x_1&+&x_2|\\
			\end{array}\right]$
	\end{enumerate}
% Problem 9
	\item Let $T(\vec{x}) = A\vec{x}$, where $A = 
		\left[\begin{array}{rrrrr}
			1&0&-1&0&1\\
			2&1&3&4&5\\
			0&1&5&4&3\\
		\end{array}\right]$\\
		Answer the following questions. \textbf{Justify precisely your answer. NO credit just for a guess!}
	\begin{enumerate}
	% Part (a)
		\item (5 Points) If $T : \mathbb{R}^n \longrightarrow \mathbb{R}^m$, then what is $n$ and what is $m$?
	% Part (b)
		\item (10 Points) Check if the vector
			$\left[\begin{array}{r}
				2\\
				0\\
				-1\\
			\end{array}\right] $ is in the range of $T$
	% Part (c)
		\item (5 Points) Find the pivot entries and pivot columns of the matrix $A$
	% Part (d)
		\item (5 Points) Check if $T$ is one-to-one
	% Part (e)
		\item (5 Points) Check if $T$ is onto
	% Part (f)
		\item (5 Points) Check if the column vectors of $A$ are linearly independent.
	\end{enumerate}
% *-o
\end{enumerate}

\end{document}